The Heavy Photon Search successfully took data during the spring 2015 Engineering and spring 2016 Physics Runs. The detectors and beam performed well and consistently with that which was proposed and simulated. This thesis presents details of the simulation and calibration of the ECal and its performance in both the Engineering and Physics runs. The first results of the unblinded, full 2015 vertex analysis using data from multiple SVT layer combinations and different SVT settings is presented. \\
\indent It has been shown that the proposal vertex reach made assumptions about the detector acceptance that are not consistent with Monte Carlo and experimental data. No reach is obtained from the Engineering Run, but the procedure for for searching for displaced vertices and the acceptance-related effects have been fully presented here. The procedure for combining the data sets from different SVT layer combinations has been discussed. The additional layers in the 0.5~mm data have too much background to have a $zCut$ that would allow these data sets to contribute to the over all reach. The additional layers of the 1.5~mm data have less background, but not enough statistics to contribute to the reach. Additionally, there are excess background events that contaminate the vertex analysis and will require further study after the improved implementation of the vertex reconstruction code in the near future. \\
\indent HPS has a promising future ahead with more beam time scheduled and planned upgrades that will improve the vertex reach. The addition of a hodoscope in front of the positron side of the ECal will improve the trigger by eliminating triggers from photons from Wide Angle Bremsstrahlung. A Layer 0 at 5~cm downstream of the target will improve the vertex resolution of the SVT by enabling tighter $zCut$s. The excess backgrounds will continue to be studied from both runs. 