Thank you to everyone who has influenced my life and scientific development during this time. This dissertation would not have been possible without the incredible mentors and colleagues I have had the pleasure to work with. Thank to you all of my HPS collaborators for building and running a successful experiment. Thank you to the Old Dominion University Physics Department for investing so much time creating a positive and stimulating environment for budding physicists.\\
\indent I would like to especially thank Larry Weinstein for being an outstanding advisor and for giving me room to explore in my research while using every opportunity to simplify and clarify new concepts. I thank Stepan Stepanyan for his guidance and direction of the HPS experiment and for organizing a supportive network at Jefferson Lab for conducting physics analysis. I also thank John Jaros for always asking questions and keeping my work relevant. Merci to Michel Gar\c con for teaching me the details of calorimetry as well as the value of a well-written analysis note. 
I thank Nathan Baltzell and Rafayel Paremuzyan for always taking the time to answer my questions and offering advice and guidance on my research. I also especially thank my collaborators at Orsay and INFN with whom I shared the exciting experience of testing and assembling a calorimeter.\\ 
\indent And finally, I thank my family and friends for their unwavering support. I thank my father for instilling in me a curiosity for the universe and the patience needed to understand complex problems. I thank my mother for giving me the gift of communication and expression through words and the perpetual drive to always move forward. I thank my brother for his support and thoughtful discussions about life as a student and scientist- may this dissertation prove that graduate school really does eventually end, (and it is actually only the beginning).\\   
\indent This dissertation is dedicated to my loving husband and best friend, Jeff, for always believing in me and supporting me in everything I do.